Wikipedia Text Mining and Entropy Analysis

### 2018-12-14 wiki_entropy/wiki_clustering.Rmd
cogsci abstract draft, clustering code and eye-tracking work added

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)

@@

```{r clustering}
##read in googlesheet
wiki_gs <- gs_title("Wikipedia_absolute")
wkpd <- gs_read(wiki_gs) %>%
  as.data.frame() %>%
  column_to_rownames(var = "language")

##do clustering
wk_clust <- wkpd %>% 
              dist() %>%
              hclust("ward.D2") %>%
              plot(hang = -1)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(klaR)

@@

```{r clustering}
##read in googlesheet
wiki_gs <- gs_title("Wikipedia_relative10")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

wkpd <- wkpd %>% 
  as.data.frame() %>%
  column_to_rownames(var = "language")

##do clustering
wk_clust <- wkpd %>% 
              dist() %>%
              hclust("ward.D2")

wk_clust %>% plot(hang = -1)
```

```{r WALS_features}
FEATURES <- c(1:144)
for (i in c(1:144)) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax

NUM_CLUSTERS <- 4

wf <- wals.feature(FEATURES)
wf %>% View()
wf <- wf[, -(1:3)]
wf <- wf[, -(ncol(wf) - 1)]
wf <- wf %>% 
  filter(language %in% LANGUAGES)
wf <- wf[, complete.cases(wf)] #this significantly trims down the dataset but is necessary for k-modes
rv <- kmodes(wf[, -(ncol(wf))], NUM_CLUSTERS, iter.max=10, weighted = FALSE)
